---
title: "Exercise 7"
author: "Your name"
date: "date"
output: 
  html_document:
    toc: yes
    toc_float: yes
    theme: cerulean
    number_sections: no
---


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(sjmisc)
library(ggplot2)

```

Follow instructions at https://kjhealy.github.io/gssr/ to install gssr

# Helper functions

Feel free to use this one in place of regular `mean`! No need to do round and na.rm=TRUE each time
```{r}
mean_round <- function(numbers,sig_digits=2){
 return(round(mean(as.numeric(numbers),na.rm=TRUE),sig_digits))
}
```



# Attach the data

Load in the data, e.g., `data(gss_all)`, `data(gss_dict)`
```{r message=FALSE, warning=FALSE}


```



# Part 1

Human evolution vs. elephant evolution

```{r warning=FALSE}


```


# Part 2

Basic science knowledge, politics, education, and endorsement of human evolution?

```{r warning=FALSE}


```


# Part 3

Work and Happiness

## 3a


```{r warning=FALSE}


```

## 3b

```{r warning=FALSE}


```

## 3c

```{r warning=FALSE}


```


# Part 4

Tax priorities


## 4a

```{r warning=FALSE}


```

## 4b

```{r warning=FALSE}


```


# Part 5

Astrology: beliefs, hobbies, and personalities


## 5a
```{r warning=FALSE}


```


## 5b
```{r warning=FALSE}


```


## 5c
```{r warning=FALSE}


```


## 5d
```{r warning=FALSE}


```
